Supplementary data for: \\textit{`MSnbase`, efficient and elegant R-based processing and visualisation of raw mass spectrometry data}

### 2020-07-02 large_experiment_processing.Rmd
Update large_experiment_processing.Rmd
Co-authored-by: Sebastian Gibb <mail@sebastiangibb.de>

The data set consists of in total `r length(fls)` mzXML files. We next load the
data using the two different `MSnbase` backends `"inMemory`" and `"onDisk"`. For
the in-memory backend, due to the larger memory requirements, we import the data
only from a subset of the files.

@@

Note that the in-memory `MSnExp` object contains only MS2 spectra (in total 
`r length(ms_mem)`) from a subset of data files, still, data import was much 
slower (over ~ 12 hours for the in-memory backend while creating the on-disk 
object from the full data data set took ~ 3 hours).

>>>>

The data set consists of `r length(fls)` mzXML files. We next load the
data using the two different `MSnbase` backends `"inMemory`" and `"onDisk"`. For
the in-memory backend, due to the larger memory requirements, we import the data
only from a subset of the files.

@@

Note that the in-memory `MSnExp` object contains only MS2 spectra (in total 
`r length(ms_mem)`) from a subset of data files. However, the data import was much 
slower (over ~ 12 hours for the in-memory backend while creating the on-disk 
object from the full data data set took ~ 3 hours).
